R Notebook

### 2023-09-27 Distribution/examples/Dune_EFT_study2/Fluxes_smeft/ProductionCoefficients_DUNE_separated/extraction.Rmd
Dune analysis program

```{r}
# Load required libraries

library(ggplot2)

v <- c(0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 0.125, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 10, 10, 10, 10, 10, 10, 10, 10, 10)

energy_values <- cumsum(v)
# List all .txt files in the current directory
file_list <- list.files(pattern = "*.txt")

# Process each file and store the results in a list
result_list <- lapply(file_list, function(file) {

  # Read the data file
  data <- read.table(file, header = FALSE)

  # Interpolate and evaluate each function
  interpolated_data <- data.frame(V1 = energy_values)
  for (i in 2:ncol(data)) {
    f <- approxfun(data$V1, data[[i]], method = "linear")
    interpolated_data[[i]] <- f(energy_values)
  }

  # Replace NaN values with 0
  interpolated_data[is.na(interpolated_data)] <- 0

  # Save the interpolated data to a new file
  write.table(interpolated_data, paste0(file),
              row.names = FALSE, col.names = FALSE, quote = FALSE)

  return(interpolated_data)
})

# Combine all interpolated data for plotting
combined_data <- do.call(rbind, result_list)

# Plot the combined interpolated functions
ggplot(combined_data, aes(x = V1)) +
  geom_line(aes(y = V2), color = "red") +
  geom_line(aes(y = V3), color = "blue") +
  geom_line(aes(y = V4), color = "green") +
  xlab("Energy") +
  ylab("Function Value")

>>>>

```{r}

vector1 = seq(2,151,6)
vector2 = seq(3,151,6)
vector3 = seq(4,151,6)
vector4 = seq(5,151,6)
vector5 = seq(6,151,6)
vector6 = seq(7,151,6)

# Set the path to the directory where the input files are located
input_dir <- "."

# Get a list of all the txt files in the directory
input_files <- list.files(input_dir, pattern = "\\.txt$", full.names = TRUE)

# Loop through the input files and extract the desired columns
for (file in input_files) {
  # Read the input file
  data <- read.table(file, header = FALSE, stringsAsFactors = FALSE)

  # Extract the desired columns and save them to separate files
  output_file1 <- paste0("plus_", basename(file))
  output_file2 <- paste0("minus_", basename(file))
  vec = c(vector1,vector2,vector3)
  vec2 =  c(vector4,vector5,vector6)
  columns1 <- c(vector1,vector2,vector3)[order(vec, decreasing = FALSE)]
  columns2 <- c(vector4,vector5,vector6)[order(vec2, decreasing = FALSE)]

  data1 <- data[, c(1, columns1)]
  data2 <- data[, c(1, columns2)]

  write.table(data1, file = output_file1, sep = "\t", quote = FALSE, row.names = FALSE,col.names = FALSE)
  write.table(data2, file = output_file2, sep = "\t", quote = FALSE, row.names = FALSE,col.names = FALSE)
}

```{r}
data <- read.table("ProdALLDpDecay.txt", header = FALSE)

### 2023-09-27 Distribution/examples/Dune_EFT_study2/xsec/detection_coefficients/interpolation.Rmd
Dune analysis program

  # Interpolate and evaluate each function
  interpolated_data <- data.frame(V1 = energy_values)
  for (i in 2:ncol(data)) {
    f <- approxfun(data$V1, data[[i]], method = "linear")
    interpolated_data[[i]] <- f(energy_values)
  }

@@

  # Save the interpolated data to a new file
  write.table(interpolated_data, paste0(file),
              row.names = FALSE, col.names = FALSE, quote = FALSE)

>>>>

  # Interpolate and evaluate each function
  interpolated_data <- data.frame(V1 = energy_values)
  for (i in 2:ncol(data)) {
    f <- approxfun(10^(data$V1), data[[i]], method = "linear")
    interpolated_data[[i]] <- f(energy_values)
  }

@@

  # Save the interpolated data to a new file
  write.table(interpolated_data, paste0("modified_",file,sep=""),
              row.names = FALSE, col.names = FALSE, quote = FALSE)
